A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-16 4_method.tex
junction placement figure

\subsubsection{Toolpath extraction algorithm}
Now that each node has a beading associated with it we can apply the beading to generate the junctions of the toolpaths.
For each upward half-edge $e$ we generate each junction $J$ based on the beading $B = B^{v_1^e}$:
\begin{align*}
J &= \{ v, w, i \} \\ 
v &= v_1^e + (v_0^e - v_1^e) \frac{R(v_1^e) - l_i^B}{R(v_1^e) - R(v_0^e)} \\ 
w &= w_i^B
% \\ i^J &= i
\end{align*}
for any $i$ for which $R(v_0^e) < l_i^B \leq R(v_1^e)$.
We store all junctions of a segment in a mapping from edge to a list of junctions.

>>>>

\subsubsection{Toolpath extraction algorithm}
Now that each node has a beading associated with it we can apply the beading to generate the junctions of the toolpaths.
For each upward half-edge $e$ we generate each junction $J$ based on the beading $B = B^{v_1^e}$:
\begin{align*}
J &= \{ v, w, i \} \\ 
v &= v_1^e + (v_0^e - v_1^e) \frac{R(v_1^e) - l_i^B}{R(v_1^e) - R(v_0^e)} \\ 
w &= w_i^B
% \\ i^J &= i
\end{align*}
for any $i$ for which $R(v_0^e) < l_i^B \leq R(v_1^e)$.
See \cref{junction_placement}.
We store all junctions of a segment in a mapping from edge to a list of junctions.

\begin{figure}
\centering
\setlength{\figheight}{.29\columnwidth}
\begin{subfigure}{0.14\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_beading.pdf}
\caption{Beadings}\label{trapezoid_beading_beading}
\end{subfigure}
\begin{subfigure}{0.5\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_propagated.pdf}
\caption{Single beading propagated to all nodes}\label{trapezoid_beading_propagated}
\end{subfigure}
\begin{subfigure}{0.34\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_separate.pdf}
\caption{Separate beadings at either top node}\label{trapezoid_beading_separate}
\end{subfigure}
\caption{
Applying beadings togenerate junctions along trapezoids.
\subref{trapezoid_beading_beading} shows half of the locations $L(n,d)_i$ and widths $W(n,d)_i$ of two arbitrary different beadings.
\subref{trapezoid_beading_propagated} shows the application of $B^1$ to the various types of trapezoid.
\subref{trapezoid_beading_separate} shows how a trapezoid with a marked edge will have two different beadings assigned, which will generate their respective junctions along the support bones.
No junctions will be generated along marked bones.
Wide black lines are outline segments, marked nodes and bones in blue, the junctions in yellow and green wavefronts of equidistant radial distance at $R = L(n,d)_i$.
}
\label{junction_placement}
\end{figure}
